---
title: "Resampling"
author: "Christopher Brown"
date: "October 5, 2015"
output: html_document
---


```{r}
set.seed(314159)
install.packages('plyr')
data(baseball, package="plyr")
install.packages("ggplot2")
install.packages('AppliedPredictiveModeling')
library('AppliedPredictiveModeling')
library(ggplot2)
```


Use the `baseball` data set from the `plyr` package for the following problem.

A very simple model to predict the number of at-bats/game **each** player has per game is given by: 
 
     abpg = sum(ab)/sum(g)  # 3.10
     

- Show that this is a bad:

```{r}
# calculate the RMSE for this model that shows the number of at-bats/game each player has per game 
install.packages('Metrics')
library("Metrics")

sqrt(mean((x[wh]-xhat[wh])^2))

attach(basebal)
library(ggplot2)

q_err <- quote (ab/g-abpg)
q_abpg <- quote ( sum(ab)/sum(g))

mean( eval(q_err, baseball), na.rm=TRUE)
hist( eval(q_err,baseball))

# residuals are not mean 0, the errors are not normally distributed 
```



- Create a better model using only number of games as a predictor

```{r}

# there are a couple of tricks here 
fit <- lm(ab~g,baseball)
summary(fit)

lm( ab~ g + 0) #<- Notice the surpression of the intercept 

```


- Calculate the "Apparent" *RMSE* of this model.    

```{r}



```


Using only Recreate the model, providing a new estimate for `ab/g` and the RMSE, using:
- 5-Fold CV
- Bootstrap

```{r}

#look at the apply function
#look at the sample funtion (replace=TRUE)

```

